---
title: "Tracking Spreadsheet"
author: "Robert M Flight"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tracking Spreadsheet}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup}
library(lubridate)
library(dplyr)
```


## Creating the Tracking Spreadsheet

I need some way to randomize the days, and then keep track of what I'm feeling
in the results.

So I will create a CSV that covers up to 50 days (40 after removing weekends),
and will randomly assign to wear shorts or pants.

I will also track what time I get to the office, when I leave, consumption
of tomatoes (I'm pretty sure I have a tomato sensitivity), and whether or not
I believe that day is a migraine day (migraines seem to make joints more sensitive
to pain in general).

```{r setup_dates}
study_frame <- data.frame(dates = (today() - 2) + seq(1, 50))
study_frame$wday <- wday(study_frame$dates)
study_frame <- filter(study_frame, !(wday %in% c(1, 7)))
```

```{r assign_pants_shorts}
study_frame$PantsOrShorts <- sample(c("Pants", "Shorts"), nrow(study_frame), replace = TRUE)
# replace the first two days, as I've already begun
study_frame$PantsOrShorts[c(1, 2)] <- c("Pants", "Shorts")
```

```{r add_other_columns}
study_frame$time_in <- 0
study_frame$time_out <- 0
study_frame$migraine <- "No"
study_frame$tomatos <- "No"
study_frame$knee_pain <- "No"
```

```{r}
write.table(study_frame, file = "study_spreadsheet.csv", row.names = FALSE, col.names = TRUE, sep = ",")
```

